\vskip-0.6in Endogenous Politics and the Design of Trade Institutions

### 2016-12-08 to-do.tex
update to-do after JIE_revision (broad strokes)
add language from JIE_revision and letter to to_do

\section{``Dynamic preferences''}
	\begin{itemize}

					\item Gul and Pesendorfer's (2001) Econometrica is a two-period model. No dynamic inconsistency; derive temptation and desire for commitment in a model with dynamically consistent preferences.
					\item Even better, especially advertising example (credit Kyle): Becker, Gary. S. and George J. Stigler, ``De Gustibus Non Est Disputandum,'' The American Economic Review, Vol. 67, No. 2 (Mar., 1977), pp. 76-90
					\item Simpler: Becker, G. S. and K. M. Murphy (1993), Simple Theory of Advertising as a Good or Bad, Quarterly Journal of Economics, 942-64.
						\begin{itemize}
							\item Their firms are my firm. Their consumers are my government
							\item Kyle's lit review talkes about `persuasive,' `informative,' and `complementary' views of advertisting. This is complementary.
							\item $e$ and $\tau$ enter objective function. Gov't is sophisticated, can make commitment that alters $e$ (i.e. behavior of another actor). But $CS + \ga(e)PS + \ldots$, just like $u(X,Y,A)$; says consumer could work to pass law about number of adds on TV each hour.
							\item Use newly drawn extensive form to explain this, lays out when welfare is realized
							\item Addresses James' concern about needing to be more precise about when $\ga$ is evaluated)
			\begin{itemize}
				\item Skeptical of comparative-static style result: can I really compare governments with different $\ga$'s?
			\end{itemize}

				\end{itemize}
			\item Mostafa, Nuno, Giovanni, Anson to some extent: Cardinal vs. ordinal
				\begin{itemize}
					\item Giovanni: if I can show properties survive  monotonic transformation, I'm fine
					\item They don't like gov't choosing its own preferences. May just need to change wording
				\end{itemize}
			\item Bob: what is fundamental structure of preferences?
			\item The way $e$ affects preferences doesn't change!!! Preferences are wrapped up in $\ga$!
			\item Devashish: Utility fcn didn't change. Just got evaluated at a different point
				\begin{itemize}
					\item Preferences don't change. It's persuasion that affects decision-making. 2nd story: Giovanni's ``expost $\ga(e)$ as effort to elect/choose ex-post decision-maker''
				\end{itemize}
		\end{itemize}

\section{Lobbying cost included in gov't welfare}
	\begin{itemize}
		\item Rick Bond: need lobbying to use up resources: if it changes net profits, it should also change $\pi$ in $W(\tau,\tau^*)$
		\item Kyle: why doesn't government (dis)value expenditure by lobby? Needs to be counted in government welfare function or justify why not
		\begin{itemize}
			\item Rohan: $(1-a)\cdot C + a \cdot W \equiv C + a \cdot (W-C)$
			\item When weights on $\pi_X$ are not linear, what are the implications for resource waste? Is it the same as $+ C / - C$?
		\end{itemize}
	\end{itemize}

@@

\section{BS2005 vs. MRC2007}
		\begin{itemize}
			\item Dangerous to build on JLS paper; better to connect to bigger cites or will limit impact, where it can be published
				\begin{itemize}
					\item Perhaps higher level model like BS GE model or some alternative approach that is not so rinky dink (my words)
				\end{itemize}
			\item I like the way you use Bagwell and Staiger (2005) as your benchmark.  But I also wondered whether Maggi and Rodriguez-Clare (2007, henceforth MRC) also offered a useful benchmark.  I know you did have comparisons to their paper in many places but it would be useful if this could be more systematic, and if your paper could draw careful parallels to your assumptions and theirs.  In both papers, the government wants to set a tariff cap in order to be able to extract rents from lobbies afterwards.  But your mechanisms seem quite different.  They have capital mobility whereas your factors are specific to each sector.  If capital is highly immobile they have a hold-up problem, which creates an incentive for lobbies to try to prevent too much liberalization under the agreement.  What drives this feature in your model?  Here I think it would be useful to explain carefully the sequence of events in your set-up more carefully.  What is the relationship between lobby effort level and tariff policy?  Is effort fixed first, after which the government sets its tariff?  If so it seems to me that would drive a kind of hold-up because lobbying effort is sunk.  It would be useful to be clearer about this so we can really understand where the results are coming from and how they compare to MRC.  Having done that, you could bring in ex-ante lobbying and treat it the same way. 
			\item In general it seems to me that you seem to "dependent" on Bagwell and Staiger... (e.g. beginning of Sections 4 and 6).
		\end{itemize}

@@

\newpage
Current structure of paper (August 25, 2016)
\begin{enumerate}
	\item Introduction
	\item Model
	\item Rigid Tariffs with Endogenous Political Pressure
		\begin{itemize}
			\item[3.1] Perfect External Enforcement. Proposition 1: weak bindings and ext. enforcement imply applied tariff = binding and may use binding to encourage or restrain lobbying
			\item[3.2] $\cdot$
				\begin{itemize}
					\item[3.2.1] $\cdot$
					\item[3.2.2] Prop 2: No ext enforcement: self enforcing implies $\tau^a \leq$ optimal binding with external enforcement
				\end{itemize}
		\end{itemize}
	\item Endogenous Political Pressure and the Escape Clause
		\begin{itemize}
			\item[4.1] Strong bindings: no cost when $\ga(e)$ only
			\item[4.2] Side payments: spirit not upheld, but IC
			\item[4.3] $\ga(s,e)$, Prop 3: lower binding never used
			\item[4.4] EC for endogenous politics
		\end{itemize}
	\item Conclusion
\end{enumerate}

>>>>

\section{``Dynamic preferences''}
	\begin{itemize}
					\item Gul and Pesendorfer's (2001) Econometrica is a two-period model. No dynamic inconsistency; derive temptation and desire for commitment in a model with dynamically consistent preferences.
					\item Even better, especially advertising example (credit Kyle): Becker, Gary. S. and George J. Stigler, ``De Gustibus Non Est Disputandum,'' The American Economic Review, Vol. 67, No. 2 (Mar., 1977), pp. 76-90
					\item Simpler: Becker, G. S. and K. M. Murphy (1993), Simple Theory of Advertising as a Good or Bad, Quarterly Journal of Economics, 942-64.
						\begin{itemize}
							\item Their firms are my firm. Their consumers are my government
							\item Kyle's lit review talkes about `persuasive,' `informative,' and `complementary' views of advertisting. This is complementary.
							\item $e$ and $\tau$ enter objective function. Gov't is sophisticated, can make commitment that alters $e$ (i.e. behavior of another actor). But $CS + \ga(e)PS + \ldots$, just like $u(X,Y,A)$; says consumer could work to pass law about number of adds on TV each hour.
							\item Use newly drawn extensive form to explain this, lays out when welfare is realized
							\item Addresses James' concern about needing to be more precise about when $\ga$ is evaluated)
			\begin{itemize}
				\item Skeptical of comparative-static style result: can I really compare governments with different $\ga$'s?
			\end{itemize}

				\end{itemize}
			\item Mostafa, Nuno, Giovanni, Anson to some extent: Cardinal vs. ordinal
				\begin{itemize}
					\item Giovanni: if I can show properties survive  monotonic transformation, I'm fine
					\item They don't like gov't choosing its own preferences. May just need to change wording
				\end{itemize}
			\item Bob: what is fundamental structure of preferences?
			\item The way $e$ affects preferences doesn't change!!! Preferences are wrapped up in $\ga$!
				\begin{itemize}
					\item ``How the assumption of a non-unitary legislature translates into this incentive constraint. In the non-unitary legislature, if the current period incentive constraint includes any future value of lobbying effort, this would mean the current-period median legislator evaluating her current-period incentive constraint using a mixture of her own political-economy weight with those of the legislators who are median in the future in the trade agreement and trade-war scenarios. The first major step I have taken to clarify the incentive constraint is the analysis in Appendix B.1 of the unitary model (described above), which I would guess is the model you had in mind. I discuss the differences between the unitary and non-unitary models in the beginning of that Appendix.''
					\item ``Note that the median legislator, whose identity is determined by the lobby's effort level $e_b$, evaluates future payoffs according to her own political economy weight, $\ga(e_b)$. Of course, depending on legislator $e_b$'s choice, either legislator $e_a$ or legislator $e_{tw}$ will be the decision maker in those future periods. But legislator $e_b$, who is the decision maker in the current period, maximizes her own welfare given the predicted behavior of future decision makers.''

				\end{itemize}
			\item Devashish: Utility fcn didn't change. Just got evaluated at a different point
				\begin{itemize}
					\item Preferences don't change. It's persuasion that affects decision-making. 2nd story: Giovanni's ``expost $\ga(e)$ as effort to elect/choose ex-post decision-maker''
				\end{itemize}
		\end{itemize}

\section{Lobbying cost included in gov't welfare}
	\begin{itemize}
		\item Rick Bond: need lobbying to use up resources: if it changes net profits, it should also change $\pi$ in $W(\tau,\tau^*)$
		\item Kyle: why doesn't government (dis)value expenditure by lobby? Needs to be counted in government welfare function or justify why not
			\begin{itemize}
				\item Rohan: $(1-a)\cdot C + a \cdot W \equiv C + a \cdot (W-C)$
				\item When weights on $\pi_X$ are not linear, what are the implications for resource waste? Is it the same as $+ C / - C$?
			\end{itemize}
		\item Try subtracting $e$ and see what it does to the graphs. Does it give me the kind of non-monotonicity I'd like? YES
			\begin{itemize}
				\item Does it do anything to the analysis?
			\end{itemize}
		\item JIE$\_$revision: I have also verified that \emph{none} of the results of the model change if lobbying effort is subtracted from the legislative/executive welfare function (except, of course, the evaluated level of welfare). I have refrained from adding the ``$-e$'' to the welfare function out of a desire to be consistent with the existing literature.
	\end{itemize}

\section{BS2005 vs. MRC2007}
		\item Review appendix of JIE$\_$revision to see what connections I want to make
		\item Dangerous to build on JLS paper; better to connect to bigger cites or will limit impact, where it can be published
				\item Perhaps higher level model like BS GE model or some alternative approach that is not so rinky dink (my words)
		\item I like the way you use Bagwell and Staiger (2005) as your benchmark.  But I also wondered whether Maggi and Rodriguez-Clare (2007, henceforth MRC) also offered a useful benchmark.  I know you did have comparisons to their paper in many places but it would be useful if this could be more systematic, and if your paper could draw careful parallels to your assumptions and theirs.  In both papers, the government wants to set a tariff cap in order to be able to extract rents from lobbies afterwards.  But your mechanisms seem quite different.  They have capital mobility whereas your factors are specific to each sector.  If capital is highly immobile they have a hold-up problem, which creates an incentive for lobbies to try to prevent too much liberalization under the agreement.  What drives this feature in your model?  Here I think it would be useful to explain carefully the sequence of events in your set-up more carefully.  What is the relationship between lobby effort level and tariff policy?  Is effort fixed first, after which the government sets its tariff?  If so it seems to me that would drive a kind of hold-up because lobbying effort is sunk.  It would be useful to be clearer about this so we can really understand where the results are coming from and how they compare to MRC.  Having done that, you could bring in ex-ante lobbying and treat it the same way. 
		\item In general it seems to me that you seem to "dependent" on Bagwell and Staiger... (e.g. beginning of Sections 4 and 6).
		\item DGH / MRC analogy from JIE$\_$revision
				\item I've supplied the suggested results to connect my model to that of Dixit, Grossman and Helpman (1997) in Appendix B.2, along with some text pointing to it at the end of Section 2.2 on page 10. The results from the DGH-style model are qualitatively different in a minor way. I discuss this difference in Appendix B.1 where I present a unitary government/legislature version of the model that most closely matches Maggi and Rodriguez-Clare 2007.
				\item The model does admit an interpretation in which the same branch of government both negotiates the trade agreement and decides on the applied tariff ex-post. In this sense, the structure of the one-shot game shares much in common with Maggi and Rodriguez-Clare 2007.
				\item The fact that the applied tariffs are equal to the negotiated binding is reminiscent of Maggi and Rodriguez-Clare 2007. Exactly the same dynamic is at play here: specifying trade agreement tariffs as caps instead of strong bindings keeps the lobby active during periods where the trade agreement is honored. In Appendix B.3, I analyze the model with strong bindings and show that the results would be altered in magnitude but not in spirit by assuming that the trade agreement tariffs are strong bindings instead of tariff caps. The only change to the model is that under strong bindings there would be zero lobbying effort during a trade agreement phase as the lobby would not need to exert effort to bid protection levels up to the trade agreement tariff. There would still be no disputes in equilibrium, but the lobbying constraint is easier to satisfy with strong bindings because the gap between trade war and trade agreement profits shrinks when the lobby stops exerting effort to receive the trade agreement tariff. Because lower trade agreement tariffs can be sustained under strong bindings, executive and legislators with small political economy weights prefer a strong-binding agreement and legislators with high political economy weights prefer a weak-binding agreement.
				\item Consider the following, alternative interpretation of the model. Assume there is only one decision-making body but the lobby is not active during the ex-ante phase, that is, when the trade agreement is being negotiated. For ease of exposition, take this single decision-making body to be the legislature so that the single decision-making body has the preferences in Expression 2. At the ex-ante stage, the welfare function would reduce to that in Expression 4. This interpretation fits into the framework of Maggi and Rodriguez-Clare 2007 by assuming that capital is perfectly mobile in the long run so that it is not worthwhile for the lobby to expend resources to influence the negotiation of the trade agreement.\footnote{To match the assumption of a social-wefare maximing executive, this requires the additional assumption that $\ga(0)=1.$ The model is qualitatively unchanged for other values of $\ga(0)$ as long as the analogue of Assumption 2 below holds.} Note that this remains a non-unitary model. Out of a single decision-making body, the level of lobbying effort determines a different decisive member depending on the situation, e.g. during ex-ante negotiations ($e=0$) versus a trade war ($e=e_{tw}$). A unitary model---in which a single actor makes different decisions depending on how much lobbying effort she experiences---results in minor, qualitative changes to the results. I discuss the unitary version of the model in Appendix B.1. Note that in either case, it is only the realization of $\ga(\cdot)$ that changes with $e$, not the preferences themselves which are embodied in $\ga(\cdot)$.
				\item The model admits this `one-branch' interpretation only if the one branch is non-unitary
				\item the model analyzed in the body of this paper can be given an interpretation in line with Maggi and Rodriguez-Clare 2007 if capital is completely mobile in the long run and the single decision-making body is non-unitary. In Appendix B.1, I compare the results of this paper to those from a model with a unitary government, as this would seem to bring the model most closely into alignment with Maggi and Rodriguez-Clare 2007 and a large part of the literature. Then, in Appendix B.2, since the government welfare function used in this paper can be interpreted as a special case of the one proposed by DGH97, I will show that a model patterned after DGH97 and specialized to this environment---which is also a unitary model---provides results that are qualitatively similar to the unitary model.
				\item I have added Appendix B.1 with analysis of the unitary model
						\item In the model with a non-unitary government, the lobby's effort $e$ determines the identity of the decision maker. Thus the decision maker at the time the lobby is pushing for the agreement to be broken ($e=e_b>e_a$ in order to have a median legislator who will break the agreement) is different from the decision maker during the trade war phase $(e = e_{tw})$ and the decision maker during a trade agreement phase ($e=e_a(\tau^a)$). The weight on the lobbying industry's profits changes with lobbying effort because lobbying effort determines a different median voter in the legislature or government more generally. However, when the median voter during a `break' phase is evaluating her incentive constraint, she values future tariff choices --- which will be determined by whoever is median in the future --- with her own preferences. Although she will not be the decision maker in the future, there is no reason for her to evaluate future welfare according to some other legislator's preference.
						\item If the model is interpreted as having a unitary government, there is only one decision maker. There is a fixed mapping from lobbying effort to the weight the decision maker places on the lobby's profits, and the realization of this weight changes with the realization of lobbying effort. Thus, predicting future lobbying effort, the decision maker knows what the realization of her weight on the lobby's profits will be and evaluates the incentive constraint accordingly. Expression (10) would be modified while the lobbying constraint is unchanged.
				\item Appendix B.2 with analysis of DGH model
						\item I claim that the government welfare function presented in this paper can be interpreted as a special case of the general welfare function proposed in DGH97. They specify government welfare as $G(a,c)$ where $a$ is the policy vector $\left(\left(\tau,\tau^*\right)\right)$ and $c$ is a vector of payments from each lobby ($e$).
						\item Here I examine a version of the DGH97 model specialized to this environment. Because the DGH97 model is fundamentally a unitary government model, the relevant benchmark is the unitary version of the model. The results of the two unitary models are qualitatively the same.
						\item To be clear about the differences, the non-unitary model examined in the body of the paper assumes that different levels of lobbying effort result in different \textit{decision-makers}. In the unitary model of DGH97, one decision maker makes different decisions depending on the level of lobbying effort. This distinction is mainly important in the context of the repeated game. Whereas the unitary decision-maker evaluates future welfare according to the lobbying effort she expects to experience in the future, the non-unitary decision-maker knows that different decision-makers will be in power and evaluates future welfare with her own preferences.
						\item In the auction-menu set-up of the DGH97 model, there does not seem to be a natural alternative to the unitary government interpretation. The lobby offers a contribution schedule of effort levels and tariffs and the government chooses among these pairs. In the non-unitary model, each different effort level determines a different government, so the government cannot choose between elements of a schedule. To analyze this model, I make the standard assumptions of a unitary government and that the lobby has all the bargaining power.
						\item Denote the government's welfare function as $W_G(\tau,\tau^*,e(\tau)) = W(\tau,\tau^*) + g(e(\tau))$ where $W = CS_X + PS_X + CS_Y + PS_Y +TR$ is social welfare. Then do analysis...
				\item Appendix B.3 with analysis of the strong binding case. 
						\item If the trade agreement involves strong bindings instead of tariff caps (i.e. weak bindings), the legislature must deliver $\tau^a$ and the lobby's optimal effort during a period in which the trade agreement holds is $e_a = 0$. That the lobby pays less---here, nothing---for the protection it receives under the trade agreement is the only change from the base model. This means that nothing changes in the trade war. Likewise the legislature's repeated-game incentive constraint is unchanged. But the lobby's incentive constraint IS changed...
						\item As in MRC, tariff caps in this model serve to keep the lobby `in the game.' A tariff cap makes the lobby's self-enforcement constraint harder to satisfy and thus requires a higher trade agreement tariff for self-enforcement. From the ex-ante point of view, strong bindings are therefore preferable. Tariff caps could be viewed as a way to commit to setting higher trade agreement tariffs and therefore as a mechanism for ensuring that rents are distributed to protectionists ex-post.

@@

@@

\vskip.5in
Current structure of paper (August 25, 2016)
\begin{enumerate}
	\item Introduction
	\item Model
	\item Rigid Tariffs with Endogenous Political Pressure
		\begin{itemize}
			\item[3.1] Perfect External Enforcement. Proposition 1: weak bindings and ext. enforcement imply applied tariff = binding and may use binding to encourage or restrain lobbying
			\item[3.2] $\cdot$
				\begin{itemize}
					\item[3.2.1] $\cdot$
					\item[3.2.2] Prop 2: No ext enforcement: self enforcing implies $\tau^a \leq$ optimal binding with external enforcement
				\end{itemize}
		\end{itemize}
	\item Endogenous Political Pressure and the Escape Clause
		\begin{itemize}
			\item[4.1] Strong bindings: no cost when $\ga(e)$ only
			\item[4.2] Side payments: spirit not upheld, but IC
			\item[4.3] $\ga(s,e)$, Prop 3: lower binding never used
			\item[4.4] EC for endogenous politics
		\end{itemize}
	\item Conclusion
\end{enumerate}
